Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-23 journal/article.tex
Work in progress

@@

>>>>

The agile practice of giving teams the power to decide was seen as an important
factor in advancing the transformation.

@@

* Management could not solve the issue of how to implement daily builds
* The teams themselves were let to figure out the technicalities
* The teams solved the technical problem management could not dictate a solution to
* It was a relevation for management that the teams were the best in solving the problem
[P5]

* Management thought initially that command and control is the way to go
* Pressure were put in points where meters were showing weakness
* A better approach was to provide the direction and let teams figure out
[P5]

* Allowing self-organization is critical in order to create commitment and engagement
[P16]

* Management drives the change
* When teams are given new responsibilities they will be naturally motivated to continue using the practices
[P18]

* It was seen as good that teams are allowed to personalize their work area
[P22]

* Recommendation: There will be vast improvements if the team is empowered
* Decision making emerges in the team.
[P27]

* Teams were given the authority to affect what was assigned to them based on
  the effort estimate they gave themselves
* Developer morale was increased and productivity was increased
* Team collaboration improved
[P30]

* Teams were empowered according to the agile manifesto --> productivity and performance rose
[P34]

* Prescribing practices led only so-far
* Effectiveness of teaching and communication was declining
* They understood that prescribing does not go any longer, and teams need to self-organize
* The teams were asked to tailor their practices instead
* The teams were asked to showcase their application of practices
* A checklist did not work --> The process needed to be tailored from team to team and between projects
* The teams were asked to tell which practices they knew to work by first hand experience
* Teams competed of showcasing best practices
[P41]

* Empowering teams successfully transfered the ownership of tailored practices to teams
[P41]

* When teams have the power to make decisions concerning development speed
  and quality, the methodology is widely accepted
[P45]

S: Empowering teams (autonomy)
